Printer ballistics through texture analysis of characters

### 2013-11-28 Printer_Ballistics.tex
Before presentation starts
Quase

%%% PREAMBLE - Do not touch %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,twocolumn,letterpaper]{article}
%%\usepackage[ansinew]{inputenc}
\usepackage[latin1,utf8]{inputenc}
\usepackage[portuges,brazil,english]{babel}
\usepackage{model}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{appendix}
\input{abaco}

\cvprfinalcopy % *** Uncomment this line for the final submission
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\ifcvprfinal\pagestyle{empty}\fi

@@

Our solution consist in getting the image of characters selected from scanned documents in grayscale, extract its properties of contrast, correlation, energy and homogeneity - creating a co-occurrence matrix - and cluster them by machine learning algorithms.

@@

As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the proprieties would be extracted. With the extracted proprieties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution. In the first instance, we needed to determine the best options for classifying the characters and attributing them to a Printer. But our final goal is not to attribute the characters to a printer, but a whole document, so in the next step, we propose a way of attributing the printer based on the classification of the characters.

\subsection{Characters Selection and Proprieties Extraction}

@@

For the proprieties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}. From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a vector of descriptors of eight values for a character. The second one gave us four per type, in other words, a sixteen sized vector.

@@

$i$ and $j$ represents the positions of the values of the co-occurrence matrix.

@@

>>>>

%%% PREAMBLE - Do not touch %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,twocolumn,letterpaper]{article}
%%\usepackage[ansinew]{inputenc}
\usepackage[latin1,utf8]{inputenc}
\usepackage[portuges,brazil,english]{babel}
\usepackage{model}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{appendix}
\input{abaco}
\makeatletter
\cvprfinalcopy % *** Uncomment this line for the final submission
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\ifcvprfinal\pagestyle{empty}\fi

@@

Our solution consist in getting the image of characters selected from scanned documents in grayscale, create a co-occurrence matrix, extract its properties of contrast, correlation, energy and homogeneity - creating a feature vector - and cluster them by machine learning algorithms.

@@

As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the properties would be extracted. With the extracted proprieties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution. In the first instance, we needed to determine the best options for classifying the characters and attributing them to a Printer. But our final goal is not to attribute the characters to a printer, but a whole document, so in the next step, we propose a way of attributing the printer based on the classification of the characters.

\subsection{Characters Selection and Properties Extraction}

@@

For the properties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}. From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a vector of descriptors of eight values for a character. The second one gave us four per type, in other words, a sixteen sized vector.

@@

$i$ and $j$ represents the value of the properties.

@@

\section{Features vectors}

\subsection{Training set}

Figure \ref{fig:feature_vector} shows a portion of the file with the feature vectors for training the classifiers.

\begin{figure*}
\begin{center}
	\includegraphics[width=2\columnwidth]{feature_vector}
	\caption{Feature vector for training.}
\label{fig:feature_vector}   
\end{center} 
\end{figure*}

Figure \ref{fig:validation} shows a portion of the file with the feature vectors for validation.

\begin{figure*}
\begin{center}
	\includegraphics[width=2\columnwidth]{validation}
	\caption{Feature vector for validation.}
\label{fig:validation}   
\end{center} 
\end{figure*}
